% the last preface section (e.g., acknowledgement.tex)
% should look like

\prefacesection{Acknowledgements}

So many people have contributed to my success during my PhD and my time as a
Research Scientist at Baidu. It's safe to say, that this thesis would not have
been possible were it not for the great collaborators I've had the good
fortune of working with and learning from and my family and friends who
supported me every day.

First, I'd like to thank my family. My entire family and especially my parents,
Lina and Yusuf, have always unconditionally supported me in my career choices
and inspired me in my work. I am also very grateful to my wife Kathy, who first
inspired me to come back to school while I was working at Google and has always
been with me every day since.

I would also like to thank my advisor Andrew Ng and co-advisor Dan Jurafsky.
Dan's constant positive encouragement, enthusiasm and mentorship over the past
six years have made the research not only possible but enjoyable.

I owe so much of my success in this work now and in the future to Andrew
directly or indirectly given that he has trained so many of my close mentors
and collaborators. Andrew has been a guide to me on all possible fronts
including technically and strategically in research and in all of the softer
skills which are critical to doing impactful work.

My first forray into machine learning research was during my time at Google,
where I had the pleasure to be mentored by Quoc Le. Quoc introduced me to the
just burgeoning field of deep learning and Andrew Ng's lab at Stanford. For
this I am very grateful. I am also grateful to Andrew Maas for taking me under
his wing during my first two years at Stanford. Andrew M. taught me a lot about
machine learning and speech recognition. During that period I also had the good
fortune of getting to know and work with many people in Andrew Ng's lab
including Chris Lengerich, Peng Qi, Richard Socher, Brody Huval, Ziang Xie,
Anshul Samar, Tao Wang, Sameep Tandon and Adam Coates.

I then spent close to two years as a Research Scientist at Baidu's newly formed
silicon valley AI lab under the leadership of Adam Coates and Andrew Ng. This
was a life changing experience for me and I couldn't be more grateful to have
had Adam Coates as a close mentor and friend during that time and since.

I'm grateful to the entire Deep Speech team. As I now know, it's a rare thing
indeed to work with such a highly productive and enjoyable group of 11 people.
The Deep Speech collaborators include Carl Case, Bryan Catanzaro, Greg Diamos,
Erich Elsen, Ryan Prenger, Sanjeev Satheesh, Shubho Sengupta, Adam Coates and
Andrew Ng. Thank you all for being a part of such an exciting time and teaching
me so much then and since.

I would also like to thank the Deep Speech 2 team at Baidu and all of my
collaborators there. There are too many to list invidually, but a few others
that I worked closely with during that time include Dario Amodei, Jesse Engel,
Eric Battenberg, Sherjil Ozair, Chong Wang, Tony Han, Jim Fan and Zhenyao Zhu.

I would also like to thank Chris Lengerich for being my collaborator and guide
in the start-up world.

After returning to Stanford from Baidu Research, I ventured into machine
learning applications for healthcare. During this time I had the good fortune
to work with Pranav Rajpurkar, Geoffrey Tison, Mintu Turakhia and several
employees at iRhythm Technologies including Masoumeh Haghpanahi, Codie Bourn
and Justin Cambra. I am also grateful to my office mates Anand Avati and Ziang
Xie as well as many other lab members including Sudnya Diamos, Dillon Laird,
Jeremy Irvin, James Liu and Will Hang.

I'd like to thank Swati Dube for kicking-off and organizing many fruitful
parternships between our lab at Stanford and other organizations. Also thanks
to the lab administrative staff and PhD student services staff for all their
help over the years.

Thanks to my reading committee James Zou, Anshul Kundaje, Dan and Andrew for
their feedback and advice as well as my thesis defense chair Nigam Shah.

Thanks to everyone who made this work possible through collaboration,
mentorship, support, encouragement and of course friendship and entertainment.

\afterpreface

